%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
% Source : https://github.com/sb2nov/resume
%------------------------

\documentclass[letterpaper,oneside,11pt]{article}
\usepackage[left=1in, right=2in, top=1in, bottom=2in, heightrounded]{geometry}

\usepackage{latexsym}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{libertine}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{lastpage}

% Adjust margins
% \addtolength{\oddsidemargin}{-0.5in}
% \addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\pagestyle{fancy}
\fancyhead{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{24pt}

% \fancyfoot[L]{\footnotesize{{Minkyoung Cho}}}
\fancyfoot[C]{\footnotesize{Page \thepage~of \pageref{LastPage}}}
\fancyfoot[R]{\footnotesize{{Last updated: Mar 9, 2025}}}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-2pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
\newcommand{\resumeItemLarger}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{0pt}}
  }
}
\newcommand{\resumeItemComment}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingSmall}[2]{
  \vspace{-2pt}\item 
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabularx}{0.97\textwidth}[t]{X@{\hspace{-5pt}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \small #4 \\
    \end{tabularx}\vspace{-6pt}
}

\newcommand{\awardsSubheading}[4]{
  \resumeSubheading{#1}{#2}{#3}{#4}\vspace{0pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-6pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Minkyoung Cho}} & minkycho@umich.edu\\
  \small{4917 BBB, 2260 Hayward Street, Ann Arbor, MI 48109} & \href{https://minkyoungcho.github.io}{https://minkyoungcho.github.io} \\
\end{tabular*}

\section{Research Interests}
\parbox{\textwidth}{Multi-Modal, Efficient AI, Robust AI, Autonomous Driving, Inference and Fine-Tuning Optimization}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  \vspace{-1pt}\item
    \begin{tabularx}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{The University of Michigan} & Ann Arbor, MI, USA \\
      \textit{\small Ph.D. Candidate in Computer Science and Engineering} & \small Aug 2022 -- Present \\
      \small Advisor: Prof. Z. Morley Mao  \\
  \end{tabularx}\vspace{-5pt}
  \vspace{-1pt}\item
      \begin{tabularx}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Korea Advanced Institute of Science and Technology (KAIST)} & Daejeon, Republic of Korea \\
        \textit{\small M.Sc. in Computer Science} & \small Mar 2015 -- Feb 2017 \\
        \small Advisor: Prof. Younghee Lee  \\
    \end{tabularx}\vspace{-5pt}
    \vspace{-1pt}\item
      \begin{tabularx}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{Ewha Womans University} & Seoul, Republic of Korea \\
        \textit{\small B.Sc. in Computer Science and Engineering} & \small Mar 2011 -- Feb 2015 \\
        \textbf{\small Summa Cum Laude}
        \textit{\small}
    \end{tabularx}\vspace{-5pt}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS-----------------
\section{Publications}
\begin{enumerate}[leftmargin=*, itemsep=0em]
  \item \small \textbf{\href{https://openreview.net/pdf?id=DKgAFfCs5F}{Cocoon: Robust Multi-Modal Perception with
  Uncertainty-Aware Sensor Fusion}} \\
  \textbf{Minkyoung Cho}, Yulong Cao, Jiachen Sun, Qingzhao Zhang, Marco Pavone, Jeong Joon Park, Heng Yang, and Z. Morley Mao\\ 
  ICLR 2025
  \item \small \textbf{\href{https://dl.acm.org/doi/abs/10.1145/3689936.3694694}{Achieving the Safety and Security of the End-to-End AV Pipeline}}\\
  Noah T. Curran, \textbf{Minkyoung Cho}, Ryan Feng, Liangkai Liu, Brian Jay Tang, Pedram MohajerAnsari, Alkim Domeke, Mert D. Pesé, and Kang G. Shin\\
  ACM CSCS Co-located with CCS 2024 
  \item \small \textbf{\href{https://arxiv.org/abs/2310.14504}{ADoPT: LiDAR Spoofing Attack Detection based on Point-Level Temporal Consistency}}\\
  \textbf{Minkyoung Cho}, Yulong Cao, Zixiang Zhou, and Z. Morley Mao\\
  BMVC 2023
  \item \small  \textbf{\href{https://arxiv.org/abs/2302.01568}{DynaMIX: Resource Optimization for DNN-Based Real-Time Applications on a Multi-Tasking System}}\\
  \textbf{Minkyoung Cho} and Kang G. Shin\\
  arXiv 2023
  \item \small \textbf{\href{https://ieeexplore.ieee.org/abstract/document/9506527}{A Novel Sensitivity Metric For Mixed-Precision Quantization With Synthetic Data Generation}}\\
  Donghyun Lee$^\ast$, \textbf{Minkyoung Cho$^\ast$}, Seungwon Lee, Joonho Song, and Changkyu Choi \\
  ICIP 2021 ($^\ast$\textbf{Equal Contribution})
  \item \small \textbf{\href{https://dl.acm.org/doi/10.1145/3008631.3008633}{Contextual Relationship-based Activity Segmentation on an Event Stream in the IoT Environment with Multi-user Activities}}\\
  \textbf{Minkyoung Cho}, Younggi Kim, and Younghee Lee\\
  ACM M4IoT Co-located with Middleware 2016
  \item \small \textbf{\href{https://ieeexplore.ieee.org/abstract/document/7524369}{Proactive Patrol Dispatch Surveillance System by Inferring Mobile Trajectories of Multiple Intruders using Binary Proximity Sensors}}\\
  Dahee Jung, \textbf{Minkyoung Cho}, Omprakash Gnawali, and HyungJune Lee\\  
  IEEE INFOCOM 2016
\end{enumerate}

%-----------PATENTS-----------------
\section{Patents}
\begin{enumerate}[leftmargin=*, itemsep=0em]
  \item \small \textbf{\href{https://patentimages.storage.googleapis.com/82/b3/b5/3652b77fd7fe2a/US20220114453A1.pdf}{Apparatus and Method for Channelwise Neural Network Compression}}\\
  Wonjo Lee, Youngmin Oh, and \textbf{Minkyoung Cho}\\
  \textit{US20220114453A1}. Published Apr. 14, 2022.
  \item \small \textbf{\href{https://patentimages.storage.googleapis.com/2a/76/c3/1436cb6d759f01/US20220108180A1.pdf}{Method for Zero-shot Pruning without Retraining}}\\
  \textbf{Minkyoung Cho}, Searom Choi, and Seungwon Lee\\
  \textit{US20220108180A1}. Published Apr. 7, 2022.
  \item \small \textbf{\href{https://patentimages.storage.googleapis.com/65/93/b5/0087b1b6fdf1bd/US20220067429A1.pdf}{Method of replacing Bilinear Interpolation with Depthwise Transposed Convolution}}\\
  Donghyeok Kwon and \textbf{Minkyoung Cho}\\
  \textit{US20220067429A1}. Published Mar. 3, 2022.
  \item \small \textbf{\href{https://patentimages.storage.googleapis.com/d4/9e/74/0f46f5127f65e5/US20210201132A1.pdf}{A Method and An Apparatus for Performing Convolution Operations}}\\
  Songyi Han, \textbf{Minkyoung Cho}, and Seungwon Lee\\
   \textit{US20210201132A1}. Published Jul. 1, 2021.
  \item \small \textbf{\href{https://patentimages.storage.googleapis.com/c1/cb/54/45c128411b5489/US20210081798A1.pdf}{Method and Apparatus for Performing Pruning of Neural Network}} \\
  \textbf{Minkyoung Cho}, Wonjo Lee, and Seungwon Lee\\
  \textit{US20210081798A1}. Published Mar. 18, 2021. \underline{$^\ast$\textbf{Mounted on Samsung Galaxy S11}}.   
\end{enumerate}
  
%-----------ACADEMIC RESEARCH EXPERIENCE-----------------
\section{Academic Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Graduate Student Research Assistant (GSRA)}{Ann Arbor, MI, USA}
    {The University of Michigan (Advisor: Prof. Z. Morley Mao)}{Aug 2022 -- Present}
    \resumeItemListStart
      \resumeItem{Efficent Fine-Tuning for Multi-Modal Models}{Developing an efficient and robust fine-tuning framework.}
      \resumeItem{Multi-Modal Perception}{Developed a robust multi-modal perception framework to guarantee reliability and accuracy in diverse driving scenarios.}
      \resumeItem{Anomaly Detection}{Developed a solution by checking temporal consistency at 3D point cloud level.}
      \resumeItem{Collaborative Perception}{Developed robust collaborative perception system across connected and automated vehicles.}
    \resumeItemListEnd
    \resumeSubheading
      {Research Intern}{Ann Arbor, MI, USA}
      {The University of Michigan (Advisor: Prof. Kang G. Shin)}{Feb 2021 -- Aug 2022}
      \resumeItemListStart
        \resumeItem{Resource Allocation}{Identified a problem in running multiple real-time vision apps on autonomous vehicle. Designed a resource optimization/allocation algorithm to satisfy apps' timing requirements.}
        \resumeItem{Neural Network Optimization}{Reduced resource and computational costs of NN models via mixed-precision quantization.}
      \resumeItemListEnd
    \resumeSubheading
      {Graduate Research Assistant}{Daejeon, Republic of Korea}
      {Computer Networks Lab, KAIST (Advisor: Prof. Younghee Lee)}{Mar 2015 -- Feb 2017}
      \resumeItemListStart
        \resumeItem{Activity Segmentation}{Designed and implemented an automated activity segmentation system using LSTM model.}
        \resumeItem{Wireless Sensor Network}{Implemented smart home/office environment using MQTT and TCP protocols, set up testbed on KAIST campus building, and managed IoT data stream from user activities.}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Research Assistant}{Seoul, Republic of Korea}
      {Intelligent Networked Systems Lab, Ewha Womans Univ. (Advisor: Prof. HyungJune Lee)}{Nov 2013 -- Dec 2014}
      \resumeItemListStart   
        \resumeItem{Proactive Patrol Dispatch Surveillance System}{Worked on two core algorithms: 1) inferring future trajectories of multiple intruders in a building and 2) maximizing the detection probability of multiple intruders while minimizing the moving distance of the patrol officers.}
        \resumeItem{Wireless Sensor Network}{Implemented TinyOS-based ZigBee network consisting of TelosB motes (binary proximity sensors) and set up testbed on Ewha campus building.}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Research Assistant}{Seoul, Republic of Korea}
      {Security and Theory of Computing Lab, Ewha Womans Univ. (Advisor: Prof. Sang-Ho Lee)}{Dec 2012 -- Feb 2013}
      \resumeItemListStart
        \resumeItem{Visual Cryptography}{Developed joint account management algorithm in mobile banking system based on visual cryptography.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------INDUSTRIAL RESEARCH EXPERIENCE-----------------
\section{Industrial Experience}
\resumeSubHeadingListStart
    \resumeSubheading
    {Deep Learning Software Intern}{Santa Clara, CA, USA}
    {NVIDIA}{Jun 2024 -- Aug 2024}
    \resumeItemListStart
      \resumeItem{Fine-Tuning Optimization}{Working on parameter-efficient fine-tuning techniques for vision and multi-modal models.}
    \resumeItemListEnd
    \resumeSubheading
      {Artificial Intelligence Researcher}{Suwon, Republic of Korea}
      {Samsung Advanced Institute of Technology @ Samsung Electronics}{Mar 2018 -- Apr 2021}
      \resumeItemListStart
        \resumeItem{Neural Network Optimization}{Designed and implemented hardware-efficient model optimization algorithms for Samsung Exynos NPU \& released on Samsung AI SDK.}
        \resumeItem{Software/hardware Co-design}{Designed and implemented a new number system for the next-generation NPU architecture.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Honors and Awards}
  \resumeSubHeadingListStart
    \awardsSubheading{Korea National Scholarship}{Mar 2015}
    {KAIST and Korea Ministry of Science and ICT}{}
    \awardsSubheading{Dean's List Award}{Apr 2012, Oct 2012, Apr 2013, Oct 2013, Apr 2014, Oct 2014}
    {Ewha Womans University}{}
    \awardsSubheading{Academic Scholarship}{Apr 2012, Oct 2012, Apr 2013, Oct 2013, Apr 2014, Oct 2014}
    {Ewha Womans University}{}
    \awardsSubheading{Han-su Scholarship}{Apr 2013}
    {Han-su Foundation}{}
  \resumeSubHeadingListEnd

%

 %--------PROGRAMMING SKILLS------------
\section{Teaching Experience}
\resumeSubHeadingListStart
  \resumeItem{Teaching}{Main TA, Introduction to Computer Networks @ KAIST, Mar 2016 - Aug 2016}
  \resumeItem{Counseling}{Counseling Assistant for CS Students @ KAIST, Sep 2015 - Aug 2016}
  \resumeItem{Tutoring}{Data Structure, Operating Systems, and Java Programming @ Ewha Womans University}
\resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Services}
\resumeSubHeadingListStart
  \resumeItem{Reading Group Organizer}{Organize Systems Reading Group @ UMich, Sep 2023 - Present}
  \resumeItem{Conference Reviewer}{BMVC'24, NeurIPSW-Compression'24, ICLR'25, ICLRW-SCOPE'25}
\resumeSubHeadingListEnd





%--------PROGRAMMING SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \resumeItem{Languages}{Python, C, Java, Markdown, \LaTeX}
   \resumeItem{Frameworks}{PyTorch, Caffe, MATLAB, Linux, TinyOS, LLVM, OpenCOOD}
 \resumeSubHeadingListEnd

\end{document}